Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-17 latex/paper.tex
Paper Minor Update

  \author{%
    Wuqiong~Zhao{\hspace{.1em}\textsuperscript{\orcidicon{0000-0002-9550-7423}}},~\IEEEmembership{Student Member, IEEE}
    \thanks{Date of publication 16 January 2024; date of current version 16 January 2024.
      The author would like to thank Lecturer Dan Yang for the guidance and help in the course of the experiment.
      The author would also like to thank AI tools including GitHub Copilot and Claude.AI for their help in preparing this paper.}
    \thanks{Wuqiong Zhao is with Southeast University, Nanjing 211189, China. (e-mail: wqzhao@seu.edu.cn, website: \url{https://wqzhao.org}).}
    \thanks{Online URL: \url{https://go.wqzhao.org/sdr-psk-fpga}}
    % \vspace{-1mm}
  }

@@

    \begin{figure*}[!t]
      \setlength{\tabcolsep}{2pt}
      \subfloat[A BPSK packet (with \textsf{Rx\_data\_tuser} is high).]{\includegraphics{_tikz_ila_BPSK-crop.pdf}}\\
      \subfloat[A QPSK packet (with \textsf{Rx\_data\_tuser} is low).]{\includegraphics{_tikz_ila_QPSK-crop.pdf}}\\
      \caption{System ILA results (some signals not shown, and this is plotted with the saved CSV data).
        The system ILA has a window of 4,096, with the ILA clock frequency of \qty{32.768}{MHz} (twice the ADC/DAC sampling rate).
        The \textcolor{myred}{red} and \textcolor{myblued}{blue} signals are at the Tx and Rx side, respectively.
        }
      \label{fig:ila}
    \end{figure*}

>>>>

  \author{%
    Wuqiong~Zhao{\hspace{.1em}\textsuperscript{\orcidicon{0000-0002-9550-7423}}},~\IEEEmembership{Student Member, IEEE}
    \thanks{Date of publication 16 January 2024; date of current version 17 January 2024.
      The author would like to thank Lecturer Dan Yang for the guidance and help in the course of the experiment.
      The author would also like to thank AI tools including GitHub Copilot and Claude.AI for their help in preparing this paper.}
    \thanks{Wuqiong Zhao is with Southeast University, Nanjing 211189, China. (e-mail: wqzhao@seu.edu.cn, website: \url{https://wqzhao.org}).}
    \thanks{Online URL: \url{https://go.wqzhao.org/sdr-psk-fpga}}
    % \vspace{-1mm}
  }

@@

    \begin{figure*}[!t]
      \setlength{\tabcolsep}{2pt}
      \subfloat[A BPSK packet (with \textsf{Rx\_data\_tuser} high).]{\includegraphics{_tikz_ila_BPSK-crop.pdf}}\\
      \subfloat[A QPSK packet (with \textsf{Rx\_data\_tuser} low).]{\includegraphics{_tikz_ila_QPSK-crop.pdf}}\\
      \caption{System ILA results (some signals not shown, and this is plotted with the saved CSV data).
        The system ILA has a window of 4,096, with the ILA clock frequency of \qty{32.768}{MHz} (twice the ADC/DAC sampling rate).
        The \textcolor{myred}{red} and \textcolor{myblued}{blue} signals are at the Tx and Rx side, respectively.
        }
      \label{fig:ila}
    \end{figure*}
